R Markdown for Reproducible Research

### 2019-01-25 paper.Rmd
fix figure reference

---
title: "R Markdown for Reproducible Research"
author: "Cole Arendt"
date: "`r Sys.Date()`"
output: pdf_document
---

@@

When creating a new document in the RStudio IDE (todo link to figure), you might notice an option
to create a "R Notebook" or "R Markdown Notebook." This is offered in addition
to the long-known "R Markdown," and the differences are subtle.

![RStudio IDE New File Dropdown showing R Markdown and R Notebook
options](./img/new-file-dropdown.png)

>>>>

---
title: "R Markdown for Reproducible Research"
author: "Cole Arendt"
date: "`r Sys.Date()`"
output: bookdown::pdf_document2
---

@@

When creating a new document in the RStudio IDE (see Figure \@ref(file-dropdown)), you might notice an option
to create a "R Notebook" or "R Markdown Notebook." This is offered in addition
to the long-known "R Markdown," and the differences are subtle.

![RStudio IDE New File Dropdown showing R Markdown and R Notebook
options](./img/new-file-dropdown.png){#file-dropdown}
